\begin{thebibliography}{1}
\bibitem{brin} Extracting Patterns and Relations from the World Wide Web. Brin, Sergey (1999) Extracting Patterns and Relations from the World Wide Web. Technical Report. Stanford InfoLab. (Publication Note: WebDB Workshop at EDBT'98)
\bibitem{mintz} Mike Mintz, Steven Bills, Rion Snow, Daniel Jurafsky: Distant supervision for relation extraction without labeled data. ACL/AFNLP 2009: 1003-1011   
\bibitem{banko} Michele Banko, Michael J. Cafarella, Stephen Soderland, Matthew Broadhead, Oren Etzioni: Open Information Extraction from the Web. IJCAI 2007: 2670-2676
\bibitem{yao} Limin Yao, Sebastian Riedel, Andrew McCallum: Unsupervised Relation Discovery with Sense Disambiguation. ACL (1) 2012: 712-720  
\bibitem{kba} {\em TREC-KBA 2012 overview slides} http://trec-kba.org/trec-kba-2012-overview.ppt
\bibitem{dalton} {\em Jeffrey Dalton, Laura Dietz}: Bi-directional Linkability From Wikipedia to Documents and Back Again. http://trec.nist.gov/pubs/trec21/papers/umass\_CIRR.kba.final.pdf
\bibitem{gebre} {\em Gebrekirstos Gebremeskel, Jiyin He, Corrado Bosscarino, Arjen de Vries}: CWI at TREC 2012, KBA Track and Session Track. http://trec.nist.gov/pubs/trec21/papers/CWI.kba.session.final.pdf
\bibitem{kjersten} {\em Brian Kjersten, Paul McNamee}: The HLTCOE Approach to the TREC 2012 KBA Track. http://trec.nist.gov/pubs/trec21/papers/hltcoe.kba.final.pdf
\bibitem{gcld} {\em Google Cross Lingual Dictionary}. http://nlp.stanford.edu/pubs/crosswikis.pdf
\end{thebibliography}
